Evidence of widspread maintenence of functional composition in vertebrate communities

### 2021-09-08 paper/manuscript.Rmd
Citation

Functional diversity metrics were calculated using the *dbFD* function from the *FD* R package.
Here we report functional richness (*FRic*), functional evenness (*FEve*), and functional diveregence (*FDiv*) which together describe three complementary characteristics of the functional space [@mason2005, @hillebrand2009].
*FRic* assesses the volume of the trait space occupied by species in the community, with higher values indicating communities with species of more extreme trait values.
*FEve* describes how species are distributed across the trait space and how abundance is distributed across species.
Higher values of *FEve* indicate more even spacing of species in the trait space and individuals across species.
*FDiv* measures the degree to which species and their abundances maximize differences in the functional space.
Higher values of *FDiv* therefore correspond to communities where many highly abundant species are on the edges of the trait space.
<!-- use these metrics because they're common, not because of their results -->

@@

All available trait data for each study were included in functional diversity calculations with the exception of traits that were the same value for all observed species in the study.
All continuous traits were z-score scaled to give each trait equal weight in the trait space [@leps2006; @schleuter2010].
The number of trait axes was limited to the maximum number of traits that fulfills the criteria $s >= s^t$, where $s$ is the number of species and \$t\$ is the number of traits.
This restriction allows for a sufficient number of axes to capture the trait space while maintaining computational feasibility.
Metrics incorporated weighting based on species abundance where available.

>>>>

Functional diversity metrics were calculated using the *dbFD* function from the *FD* R package [@laliberté2010]. Here we report functional richness (FRic), functional evenness (FEve), and functional diveregence (FDiv) which together describe three complementary characteristics of the functional space [@mason2005, @hillebrand2009]. FRic assesses the volume of the trait space occupied by species in the community, with higher values indicating communities with species of more extreme trait values. FEve describes how species are distributed across the trait space and how abundance is distributed across species. Higher values of FEve indicate more even spacing of species in the trait space and individuals across species. FDiv measures the degree to which species and their abundances maximize differences in the functional space. Higher values of FDiv therefore correspond to communities where many highly abundant species are on the edges of the trait space. <!-- use these metrics because they're common, not because of their results -->

@@

All available trait data for each study were included in functional diversity calculations with the exception of traits that were the same value for all observed species in the study.
All continuous traits were z-score scaled to give each trait equal weight in the trait space [@leps2006; @schleuter2010].
The number of trait axes was limited to the maximum number of traits that fulfills the criteria $s >= s^t$, where $s$ is the number of species and *t* is the number of traits.
This restriction allows for a sufficient number of axes to capture the trait space while maintaining computational feasibility.
Metrics incorporated weighting based on species abundance where available.
